---
title: "OSAC text"
output:
  word_document:
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r, include=F}
### THIS TEMPLATE IS FOR ONE BANK ONLY. FOR A FRESH OSAC RUN, COPY AND PASTE THE TEMPLATE FOR EACH BANK, AND EDIT ACCORDINGLY. 
### THE TEMPLATE ASSUMES THAT FISHING OCCURRED, AND THAT MEAT COUNT DATA ARE AVAILABLE
### BOLDED CODE GENERALLY NEEDS UPDATING. SAVE THE ANNUAL RESULT IN Y:/Offshore/Assessment/YYYY/PRESENTATIONS/OSAC/
### THE POWERPOINT PRESENTATION IS NOT GENERATED AUTOMATICALLY. USE SURVEY SUMMARY PPTX AND LAST YEAR'S VERSION. 


year <- 2022
direct <- "Y:/Offshore/Assessment/"
direct_fns <- "C:/Users/keyserf/Documents/Github/Assessment_fns/"
load(paste0(direct, "Data/Fishery_data/Summary/", year, "/OSAC_summary.Rdata"))
load(paste0(direct, "Data/Fishery_data/Summary/", year, "/OSAC_tidy_logs.Rdata"))
load(paste0(direct, "Data/Survey_data/", year, "/Survey_summary_output/Survey_all_results.Rdata"))

options(scipen=999)

fish.res[,2:13] <- apply(fish.res[,2:13], 2, function(x) as.numeric(as.character(x)))
sum.stat <- dplyr::rename(sum.stat, bank=Bank)

require(plyr)
require(tidyverse)

cpue.dat <- plyr::ldply(cpue.dat)
cpue.dat <- dplyr::rename(cpue.dat, bank=.id)
LTMs <- plyr::ddply(.data=cpue.dat, .(bank),
              summarize,
              catchLTM = median(catch, na.rm=T),
              effortLTM = median(effort, na.rm=T),
              cpueLTM = median(cpue, na.rm=T))
LY <- ddply(.data=cpue.dat[cpue.dat$year==year-1,], .(bank),
            summarize,
            catchLY = catch,
            effortLY = effort,
            cpueLY = cpue)


# 2020 will not work in Survey_summary_word.R without major changes. Try to do it manually instead. 
fish.reg <- read.csv(paste(direct,"Data/Fishery_regulations_by_bank.csv",sep=""))

sizes <- fish.reg %>%
  filter(year==2022) %>%
  group_by(Bank)%>%
  mutate(MC = MC_reg) %>%
  select(Bank, MC)


meanSH <- NULL
for (i in names(surv.Rand)[which(names(surv.Rand) %in% sizes$Bank)]){
  if(!i =="Ger") CS <- survey.obj[[i]]$model.dat$CS[survey.obj[[i]]$model.dat$year==year]
  if(i =="Ger") CS <- lined.survey.obj$model.dat$CS[lined.survey.obj$model.dat$year==year]
  CSmin <- which(names(surv.Rand[[i]]) == paste0("h", CS))
  CSmax <-  which(names(surv.Rand[[i]]) == "h200")
  meanSH[[i]] <- mean(apply(surv.Rand[[i]][surv.Rand[[i]]$year %in% year, CSmin:CSmax], 1, function(x) sum(x*seq((CS-2.5),197.5,5))/sum(x)), na.rm=T)
}


require(pander)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)

```

# **YYYY OSAC** - `r Sys.time()`

## **Outline**
1.	This is an outline of the various banks that we’ll be discussing today. All of the banks except Middle and Sable Banks were fished this year.

2.	Note that the fishery data comes from logs and reports that we were able to verify up to october 15, `r year`
_IMPORTANT We have an agreement in place with offshore valid until end of Dec 2020 to show all data (including any banks with less than 5 trips) so no need to alter anything due to privacy.  In 2020 we will need to get that agreement resigned by all the players!!!_


## **Bank name:**

1.	Management
    a.	The TAC on **Bank name** in `r year` was **XXX** tonnes
    b.	the Meat count regulation was `r sizes[sizes$Bank==bank,]$MC` scallops per 500 grams of meat (about 13 grams per scallop)

<br>

2.	Fishery
    a.	There were n=`r fish.res$WF.trips[fish.res$bank==bank] + fish.res$FT.trips[fish.res$bank==bank]` trips on Browns Bank North in `r year`
        i.	Numbers here are verified logs up to October 15, `r year`
        ii.	Last trip was ≈ `r format(max(fish.dat$fished[fish.dat$bank==bank & fish.dat$year==year]), "%d-%b-%Y")`
    b.	Total catch was `r round(fish.res$catch[fish.res$bank==bank], 0)` tonnes
    c.	Total effort was `r round(fish.res$effort[fish.res$bank==bank], 0)` hm
    d.	The CPUE was **above** the bank median, coming in at `r round(fish.res$cpue[fish.res$bank==bank], 1)` kg/hm
    e.	The average fishery meat count was `r round(meat.count$summarytable$mean[meat.count$summarytable$bank=="brownsnorth" &  meat.count$summarytable$fleet=="all"], 1)` scallops per 500 grams of meat.
            i.	These would be an average of `r round(500/meat.count$summarytable$mean[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="all"],1)` gram scallops.
    f.The range was `r floor(round(meat.count$summarytable$min[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="all"], 1))` to `r ceiling(round(meat.count$summarytable$max[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="all"], 1))`

    f.	There were `r fish.res$FT.trip[fish.res$bank==bank]` FT trips and `r fish.res$WF.trip[fish.res$bank==bank]` WF trips
        i.	FT fleet caught `r round(fish.res$FT.catch[fish.res$bank==bank], 0)`  tonnes  while WF fleet caught `r round(fish.res$WF.catch[fish.res$bank==bank], 1)` tonnes
        ii.	FT CPUE was `r round(fish.res$FT.cpue[fish.res$bank==bank], 1)` kg/hm, and WF CPUE was `r round(fish.res$WF.cpue[fish.res$bank==bank], 1)` kg/hm
        iv. FT meat count was `r round(meat.count$summarytable$mean[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="FT"], 1)` scallops per 500g of meat on average. FT meat counts ranged from `r floor(round(meat.count$summarytable$min[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="FT"], 1))` - `r ceiling(round(meat.count$summarytable$max[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="FT"], 1))` scallops per 500g of meat
        v.	WF meat count was `r round(meat.count$summarytable$mean[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="WF"], 1)` scallops per 500g of meat. WF meat counts ranged from `r floor(round(meat.count$summarytable$min[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="WF"], 1))` - `r ceiling(round(meat.count$summarytable$max[meat.count$summarytable$bank=="brownsnorth" & meat.count$summarytable$fleet=="WF"], 1))` scallops per 500g of meat

<br>

11.	So now we'll look at the fishery time series figures
    a. Catch and effort were **below** their long term medians in `r year`, and CPUE was **above** its long term median
    b. _Remember the standard error bars represent our confidence in the mean estimate for the bank CPUE, wider indicates years in which catch was more variable_
    c. _Note different fleets_

<br>

12.	Fishery spatial
    a.	Now we will at the catch spatially,
        i.	grouped into “1 minute” cells
        ii. The darker the colour, the higher the catch in that cell
    b.	**There were 6 trips on XXXXX in `r year`**
    d.	There were `r length(fish.cells$catch[fish.cells$bank==bank & fish.cells$catch>5])` cells above 5 tonnes of catch in `r year`. Catch ranged from `r round(sum.stat$min.catch[sum.stat$bank==bank],2)` –  `r round(sum.stat$max.catch[sum.stat$bank==bank],2)` tonnes. Median catch was `r round(sum.stat$median.catch[sum.stat$bank==bank],2)`.
```{r, echo=F, message=F}
pander::pander(plyr::join(sum.stat[sum.stat$bank==bank,], fish.res[fish.res$bank==bank,], type="full"))
```

<br>

```{r, echo=F}
knitr::kable(meat.count$summarytable[meat.count$summarytable$bank=="brownsnorth",], row.names=F, digits=4)
```

<br>

```{r, echo=F}
knitr::kable(LY[LY$bank==bank,], row.names=F, digits=4)
```

<br>
```{r, echo=F}
knitr::kable(LTMs[LTMs$bank==bank,], row.names=F, digits=4)
```


<br>

INSERT SURVEY NOTES

<br>

11. **So the outlook for XXXXXXX**
    a. **From the fishery data, CPUE was XXXXX the long term median**
    b. **And from the survey data, Pre-recruit abundance was XXXXX the long term median**
    c. **Recruit and fully-recruited abundance and biomass were XXXXX their long term medians**
    d. **condition factor was XXXXX the LTM.**

