---
title: "Update model scenarios 2022"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    orientation: columns
---

```{r, include=F}
require(patchwork)
require(ggplot2)
require(tidyverse)
require(forecast)
direct <- "Y:/Offshore/Assessment/"
direct_fns <- "C:/Users/keyserf/Documents/Github/Assessment_fns/"
direct_out <- "C:/Users/keyserf/Documents/"
yr <- 2021 # survey year
banks <- c("GBa", "BBn")
imputetype <- c("mixed", "min", "max", "LTM", "previous_year", "midpoint")
proj.box<-NULL
fit <- NULL
biomass <- NULL
res <- NULL
perc.diff.pre2020 <- NULL
perc.diff <- NULL
old.model <- NULL
TS<- NULL
ACF <- NULL
for(b in banks){
  
  # for comparing past pre-2020 model output to new post-2020 model output
  old <- (load(paste0(direct_out, "Data/Model/",2020,"/",b,"/Results/Final_model_results.RData",sep="")))
  
  DD.plt.19 <- DD.out[[b]]
  
  DD.gg.19 <- data.frame(year=yrs[[b]], bank=b, impute="pre2020", 
                         B=DD.plt.19$median$B, q=DD.plt.19$median$q, R=DD.plt.19$median$R,
                         qU=DD.plt.19$median$qU, I=DD.plt.19$data$I, IR = DD.plt.19$data$IR, 
                         U=DD.plt.19$data$U, I.cv=DD.plt.19$data$I.cv,
                         IR.cv=DD.plt.19$data$IR.cv, U.cv=DD.plt.19$data$U.cv,
                         g=DD.plt.19$data$g,
                         gR=DD.plt.19$data$gR,
                         clappers=DD.plt.19$data$clappers,
                         clappersR=DD.plt.19$data$clappersR,
                         m=DD.plt.19$median$m,
                         mR=DD.plt.19$median$mR,
                         CF=DD.dat$CF, 
                         l.bar=DD.dat$l.bar)
 
  old.model[[b]] <- DD.gg.19
  
  #remove objects read in from 2020 model
  rm(list=ls()[which(ls() %in% old)])
  
  for(it in imputetype){
    # this loads the 2022 model data and get the file names. The parentheses are correct!!
    yr <- 2021 # survey year
    objs <- (load(paste0(direct_out, "Data/Model/",(yr+1),"/",b,"/Results/Model_testing_results_", it, ".RData",sep="")))
    
    # set 2020 values to NA. Should I do this for model output or no?
    DD.plt <- DD.out[[b]]
    DD.plt$median$B[which(yrs[[b]]==2020)] <- NA
    DD.plt$sims.list$B[,which(yrs[[b]]==2020)] <- NA
    DD.plt$median$R[which(yrs[[b]]==2020)] <- NA
    DD.plt$sims.list$R[,which(yrs[[b]]==2020)] <- NA
    DD.plt$data$I[which(yrs[[b]]==2020)] <- NA
    DD.plt$data$IR[which(yrs[[b]]==2020)] <- NA
    DD.plt$data$clappers[which(yrs[[b]]==2020)] <- NA
    DD.plt$data$clappersR[which(yrs[[b]]==2020)] <- NA
    
    DD.gg <- data.frame(year=yrs[[b]], bank=b, impute=it, 
                        B=DD.plt$median$B, q=DD.plt$median$q,
                        R=DD.plt$median$R, qU=DD.plt$median$qU, 
                        I=DD.plt$data$I, IR = DD.plt$data$IR, 
                        U=DD.plt$data$U,
                        I.cv=DD.plt$data$I.cv,
                        IR.cv=DD.plt$data$IR.cv, 
                        U.cv=DD.plt$data$U.cv,
                        g=DD.plt$data$g,
                        gR=DD.plt$data$gR,
                        m=DD.plt$median$m,
                        mR=DD.plt$median$mR,
                        clappers=DD.plt$data$clappers,
                        clappersR=DD.plt$data$clappersR,
                        CF=DD.dat$CF,
                        l.bar=DD.dat$l.bar) 
    
    # for biomass projection
    TACI<-which(DD.out[[b]]$data$C.p==TACi[[b]]+proj.catch[[b]])
    proj <- data.frame(year=2022, B.p=DD.out[[b]]$sims.list$B.p[,TACI], tac=TACi[[b]]+proj.catch[[b]])
    proj.q <- proj$B.p[proj$B.p>quantile(proj$B.p,0.1)&proj$B.p<quantile(proj$B.p,1-0.1)]
    proj.q <- data.frame(year=2022, vals = boxplot(proj.q)$stats, labs=c("y0", "y10", "y50", "y90", "y100"))
    proj.q <- pivot_wider(proj.q, values_from = vals, names_from=labs)
    proj.q <- data.frame(proj.q, bank=b, impute=it)
    
    # to compare post-2020 to pre-2020 results. Need to figure out which variables are actually relevant and make sure I'm using the right ones
    diff.per <- (DD.gg[DD.gg$year<2020, c("B", "q", "R", "qU", "g", "gR", "m", "mR")] -
                   DD.gg.19[, c("B", "q", "R", "qU", "g", "gR", "m", "mR")])/
      DD.gg.19[, c("B", "q", "R", "qU","g", "gR", "m", "mR")]
    
    diff.per <- cbind(DD.gg[DD.gg$year<2020, c("year", "bank", "impute")], 
                      diff.per)
    
    res <- rbind(res, DD.gg)
    proj.box <- rbind(proj.box, proj.q)
    perc.diff.pre2020 <- rbind(perc.diff.pre2020, diff.per)
    
  }
  
  fitB <- ggplot() +
    geom_point(data=unique(res[res$bank==b,c("year", "I")]), aes(x=year, y=I))+
    geom_segment(data=unique(res[res$bank==b,c("year", "I", "I.cv")]), aes(x=year, xend=year, y=I-I.cv*I, yend=I+I.cv*I)) +
    geom_line(data=res[res$bank==b,], aes(x=year, y=B*q, colour=impute)) + ylab("Fully recruited biomass") +
    geom_line(data=res[res$year%in%c(2019, 2021) & res$bank==b,], aes(year, B*q, colour=impute), linetype="dashed") +
    #ylim(0,8000) +
    theme_bw() 
  
  fitR <- ggplot() + 
    geom_point(data=unique(res[res$bank==b,c("year", "IR")]), aes(x=year, y=IR))+
    geom_segment(data=unique(res[res$bank==b,c("year", "IR", "IR.cv")]), aes(x=year, xend=year, y=IR-IR.cv*IR, yend=IR+IR.cv*IR)) +
    geom_line(data=res[res$bank==b,], aes(x=year, y=R*q, colour=impute)) + ylab("Recruit biomass") +
    geom_line(data=res[res$year%in%c(2019, 2021) & res$bank==b,], aes(year, R*q, colour=impute), linetype="dashed") +
    #ylim(0,2100)+
    theme_bw()
  
  fitU <- ggplot() +
    geom_point(data=unique(res[res$bank==b,c("year", "U")]), aes(x=year, y=U))+
    geom_line(data=res[res$bank==b,], aes(x=year, y=B*qU, colour=impute)) + ylab("CPUE") +
    geom_line(data=res[res$year%in%c(2019, 2021) & res$bank==b,], aes(year, B*qU, colour=impute), linetype="dashed") +
    #geom_segment(data=res, aes(x=year, xend=year, y=U-U.cv*U, yend=U+U.cv*U), colour="red") +
    #ylim(0,75)+
    theme_bw()
  
  fit[[b]] <- fitB / fitR / fitU
  png(paste0("Y:/Offshore/Assessment/2022/Updates/", b, "/Figures_and_tables/fit_comp.png"), units="in", height=8, width=7, res=400)
  print(fit[[b]])
  dev.off()
  
  biomass[[b]] <- ggplot() + geom_line(data=res[res$bank==b,], aes(x=year, y=B, colour=impute)) + geom_point(data=res[res$bank==b,], aes(x=year, y=B, colour=impute, shape=impute)) + 
    geom_boxplot(data=proj.box[proj.box$bank==b,], aes(x=year, ymin=y0, lower=y10, middle=y50, upper=y90, ymax=y100, colour=impute), width=1.5, stat="identity") +
    geom_line(data=res[res$year%in%c(2019, 2021) & res$bank==b,], aes(year, B, colour=impute), linetype="dashed") +
    theme_bw() #+
  # ylim(0,25000)
  png(paste0("Y:/Offshore/Assessment/2022/Updates/", b, "/Figures_and_tables/biomass_comp.png"), units = "in", height=6, width=9, res=400)
  print(biomass[[b]])
  dev.off()
  
  longer <- pivot_longer(perc.diff.pre2020[perc.diff.pre2020$bank==b,], cols = c("B", "q", "R", "qU", "m", "mR"))
  longer$name <- factor(longer$name, levels=c("B", "R", "q", "qU", "m", "mR"))
  perc.diff[[b]] <- ggplot() + geom_line(data=longer, aes(year, value, colour=impute)) +
    facet_wrap(~name, scales="free_y", nrow=3) +
    theme_bw() +
    ylab("proportional difference")
  
  png(paste0("Y:/Offshore/Assessment/2022/Updates/", b, "/Figures_and_tables/perc_diff.png"), units="in", height=8, width=7, res=400)
  print(perc.diff[[b]])
  dev.off()
  
  ### model inputs
  survey <- pivot_longer(old.model[[b]], cols = c("I", "IR", "clappers", "clappersR", "CF", "l.bar")) 
  survey$name <- factor(survey$name, levels=c("I", "IR", "clappers", "clappersR", "CF", "l.bar"))
  
  TS[[b]] <- ggplot() + geom_line(data=survey, aes(year, value)) +
    facet_wrap(~name, scales="free_y", nrow=3) +
    theme_bw()
  
  png(paste0("Y:/Offshore/Assessment/2022/Updates/", b, "/Figures_and_tables/TS.png"), units="in", height=8, width=7, res=400)
  print(TS[[b]])
  dev.off()
  
  ACF[[b]] <- ggAcf(old.model[[b]]$I) + theme_bw() + ggtitle("I") +
    ggAcf(old.model[[b]]$IR) + theme_bw() + ggtitle("IR") +
    ggAcf(old.model[[b]]$clappers) + theme_bw() + ggtitle("clappers") +
    ggAcf(old.model[[b]]$clappersR) + theme_bw() + ggtitle("clappersR") +
    ggAcf(old.model[[b]]$CF) + theme_bw() + ggtitle("CF") +
    ggAcf(old.model[[b]]$l.bar) + theme_bw() + ggtitle("l.bar") +
    plot_layout(ncol=2)
  
  png(paste0("Y:/Offshore/Assessment/2022/Updates/", b, "/Figures_and_tables/ACF.png"), units="in", height=8, width=7, res=400)
  print(ACF[[b]])
  dev.off()
  
  
}

```


Sidebar {.sidebar}
=================================================================

* I & IR = survey index  

* B & R = biomass from model  

* U = CPUE  

* g & gR = growth  

* m & mR = mortality  

* q = survey catchability  

* qU = fishery catchability CPUE


GBa Data Inputs
====================================================================

Column {data-width=500}
------------------------------------------------

### Time series 

```{r}
TS$GBa
```


Column {data-width=500}
-------------------------------------------------

### ACF

```{r}
ACF$GBa
```



GBa Model Results
====================================================================

Column {data-width=400}
------------------------------------------------

### Fit 

```{r, fig.width=6, fig.asp=1.5}
fit$GBa
```


Column {data-width=600}
-------------------------------------------------

### Biomass projection

```{r, fig.width=7, fig.asp=0.5}
biomass$GBa
```


### Difference from 2020 model

```{r, fig.width=7, fig.asp=0.5}
perc.diff$GBa
```


BBn Data Inputs
====================================================================

Column {data-width=500}
------------------------------------------------

### Time series 

```{r}
TS$BBn
```


Column {data-width=500}
-------------------------------------------------

### ACF

```{r}
ACF$BBn
```



BBn Model Results
=========================================================================

Column {data-width=400}
------------------------------------------------

### Fit

```{r, fig.width=6, fig.asp=1.5}
fit$BBn
```


Column {data-width=600}
-------------------------------------------------

### Biomass projection

```{r, fig.width=7, fig.asp=0.5}
biomass$BBn
```

### Difference from 2020 model

```{r, fig.width=7, fig.asp=0.5}
perc.diff$BBn
```
