---
output: 
  pdf_document:
    fig_caption: yes
    extra_dependencies: ["float"]
linkcolor: blue
params:
  bank: NA
  banknum: NA
header-includes:
 - \usepackage{float}
---

```{r, echo=F, message=F, warning=F}
knitr::opts_knit$set(eval.after = "fig.cap")
knitr::opts_chunk$set(fig.pos = 'H')
options(knitr.kable.NA = '')
require(tidyverse)
options(tinytex.verbose = TRUE)


year <- 2021

load("summary.Rdata")
source(paste0(direct_fns, "/Other_functions/ScallopRound.R"))

ntows <- summary_data$ntows
highlights <- summary_data$highlights
sizes <- summary_data$sizes
dates <- summary_data$dates
yeartable <- summary_data$yeartable
spatial.sum.stats <- summary_data$spatial.sum.stats

bank <- data.frame(lab = c("Ban", "BanIce", "Mid", "Sab", "Ger", "BBn", "BBs", "GB", "GBa", "GBb"), name=NA)
bank$name[bank$lab=="Ban"] <- "Banquereau (Sea scallop)"
bank$name[bank$lab=="BanIce"] <- "Banquereau (Icelandic scallop)"
bank$name[bank$lab=="Mid"] <- "Middle Bank"
bank$name[bank$lab=="Sab"] <- "Sable Bank"
bank$name[bank$lab=="Ger"] <- "German Bank"
bank$name[bank$lab=="BBn"] <- "Browns Bank North"
bank$name[bank$lab=="BBs"] <- "Browns Bank South"
bank$name[bank$lab=="GB"] <- "Georges Bank (monitoring stations)"
bank$name[bank$lab=="GBa"] <- "Georges Bank 'a'"
bank$name[bank$lab=="GBb"] <- "Georges Bank 'b'"

bankname <- bank$name[bank$lab==params$bank]
bank$towtype1[bank$lab %in% c("Ban", "BanIce", "GB", "Mid")] <- "fixed"
bank$towtype1[bank$lab %in% c("BBn", "BBs", "GBa", "GBb", "Sab")] <- "stratified random"
bank$towtype1[bank$lab=="Ger"] <- "random"

if(length(ntows$Freq[ntows$bank==params$bank])==2 & !params$bank %in% c("Ger", "GB")) surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==1], " ", bank$towtype1[bank$lab==params$bank],  " stations, and ", ntows$Freq[ntows$bank==params$bank & !ntows$Var1==1], " ", "exploratory stations.")
if(length(ntows$Freq[ntows$bank==params$bank])==1 & !params$bank == "Ger") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==1], " ", bank$towtype1[bank$lab==params$bank],  " stations.")
if(length(ntows$Freq[ntows$bank==params$bank])==2 & params$bank == "Ger") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==1], " ", bank$towtype1[bank$lab==params$bank],  " stations within the survey domain, and ", ntows$Freq[ntows$bank==params$bank & ntows$Var1==3], " ", "stations repeated from the previous survey.")
if(length(ntows$Freq[ntows$bank==params$bank])>2 & params$bank == "Ger") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==1], " ", bank$towtype1[bank$lab==params$bank],  " stations within the survey domain, and ", ntows$Freq[ntows$bank==params$bank & ntows$Var1==3], " ", "stations repeated from the previous survey, and ", ntows$Freq[ntows$bank==params$bank & !ntows$Var1 %in% c(1, 3)], " exploratory stations.")
if(length(ntows$Freq[ntows$bank==params$bank])==2 & params$bank =="GB") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==3], " ", bank$towtype1[bank$lab==params$bank],  " stations, and ", ntows$Freq[ntows$bank==params$bank & !ntows$Var1==3], " ", "exploratory stations.")
if(length(ntows$Freq[ntows$bank==params$bank])==1 & params$bank =="GB") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==3], " ", bank$towtype1[bank$lab==params$bank],  " stations.")


if(params$bank=="Ger") bank$towtype1[bank$lab==params$bank] <- "sampling with partial replacement"

maxbin <- strsplit(highlights$word[highlights$variable=="maxbin" & highlights$bank==params$bank], "(", fixed=T)[[1]][1]

mwshltm <- strsplit(highlights$nearLTM[highlights$variable=="CF" & highlights$bank==params$bank], " (", fixed=T)[[1]][1]

tabnum <- 5*(params$banknum-1) + 1:5
fignum <- 12*(params$banknum-1) + 1:12

table <- highlights[#highlights$bank==params$bank & 
  highlights$variable %in% c("NPR", "NR", "N", "IPR", "IR", "I"), ]

table$word[as.numeric(table$thisyearraw) < as.numeric(table$lastyearraw)] <- "decreased"
table$word[as.numeric(table$thisyearraw) > as.numeric(table$lastyearraw)] <- "increased"

table$perc[table$word=="increased"] <- 
  (as.numeric(table$thisyearraw[table$word=="increased"]) - as.numeric(table$lastyearraw[table$word=="increased"]))/
  as.numeric(table$thisyearraw[table$word=="increased"]) *100

table$perc[table$word=="decreased"] <-   
  (as.numeric(table$lastyearraw[table$word=="decreased"]) - as.numeric(table$thisyearraw[table$word=="decreased"]))/
  as.numeric(table$lastyearraw[table$word=="decreased"]) *100

table$perclab <- ScallopRound(table$perc, 2)

table$perclab[table$perc>0 & table$perc < 0.01] <- "<0.01"
table$perclab[table$perc>99] <- ">99"

table$state <- paste0(table$word, " by ", table$perclab, "% since")

table$state[is.na(table$perc)] <- "was similar to"

highlights$lastyear[highlights$variable %in% c("N", "NR", "NPR", "I", "IR", "IPR", "Nclap", "NRclap", "NPRclap", "PRpercentclap", "Rpercentclap", "Cpercentclap") & !is.na(highlights$lastyearraw) & (highlights$lastyearraw>0 & highlights$lastyearraw<0.01)] <- "<0.01"
highlights$thisyear[highlights$variable %in% c("N", "NR", "NPR", "I", "IR", "IPR", "Nclap", "NRclap", "NPRclap", "PRpercentclap", "Rpercentclap", "Cpercentclap") & !is.na(highlights$thisyearraw) & (highlights$thisyearraw>0 & highlights$thisyearraw<0.01)] <- "<0.01"
highlights$LTM[highlights$variable %in% c("N", "NR", "NPR", "I", "IR", "IPR", "Nclap", "NRclap", "NPRclap", "PRpercentclap", "Rpercentclap", "Cpercentclap") & !is.na(highlights$LTMraw) & (highlights$LTMraw>0 & highlights$LTMraw<0.01)] <- "<0.01"


```

\newpage


# `r bankname` {#`r paste0(params$bank, "links")`}

**`r year` Summary**

-  Pre-recruit abundance `r table$state[table$bank==params$bank & table$variable == "NPR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r table$nearLTM[table$bank==params$bank & table$variable == "NPR"]` the long term median. 
-  Recruit abundance `r table$state[table$bank==params$bank & table$variable == "NR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r table$nearLTM[table$bank==params$bank & table$variable == "NR"]` the long term median.
-  Fully-recruited abundance `r table$state[table$bank==params$bank & table$variable == "N"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r table$nearLTM[table$bank==params$bank & table$variable == "N"]` the long term median.


-  Pre-recruit biomass `r table$state[table$bank==params$bank & table$variable == "IPR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r table$nearLTM[table$bank==params$bank & table$variable == "IPR"]` the long term median.
-  Recruit biomass `r table$state[table$bank==params$bank & table$variable == "IR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r table$nearLTM[table$bank==params$bank & table$variable == "IR"]` the long term median.
-  Fully-recruited biomass `r table$state[table$bank==params$bank & table$variable == "I"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r table$nearLTM[table$bank==params$bank & table$variable == "I"]` the long term median.


- Condition factor `r highlights$word[highlights$variable=="CF" & highlights$bank==params$bank]` since `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r mwshltm` the long term median.


**Sections**

- [Survey design & analysis](#`r paste0(params$bank, "SD")`)  

- [Abundance & biomass time series summary](#`r paste0(params$bank, "ABTS")`)  

- [Shell height frequencies](#`r paste0(params$bank, "SHF")`)  

- [Meat weight-shell height & condition](#`r paste0(params$bank, "MWSH")`)  

- [Spatial distribution maps](#`r paste0(params$bank, "map")`)  

- [Clapper time series](#`r paste0(params$bank, "clap")`)  

- [Biomass, meat count, and shell height relationship](#`r paste0(params$bank, "breakdown")`)  

- [Return to Table of Contents](#toc)


\newpage


## Survey Design & Analysis {#`r paste0(params$bank, "SD")`}

The survey of `r bankname` in `r year` used a `r bank$towtype1[bank$lab==params$bank]` survey design (Figure `r fignum[1]`). There were `r surv.description`

In the `r bankname` survey, pre-recruits are considered to be scallops with shell heights less than `r sizes$RS[sizes$bank==params$bank]$size` mm, recruits have shell heights from `r sizes$RS[sizes$bank==params$bank]$size` mm to `r sizes$CS[sizes$bank==params$bank]$size` mm, and fully-recruited scallop have shell heights greater than `r sizes$CS[sizes$bank==params$bank]$size` mm. 

[Return to bank summary](#`r paste0(params$bank, "links")`)
\newpage


## Abundance & biomass time series summary {#`r paste0(params$bank, "ABTS")`}

```{r, echo=FALSE}
if(params$bank %in% c("Ban", "BanIce", "Mid", "GB")) fig1foot <- paste0("Note that error bars are not calculated for fixed station survey designs as they do not properly account for uncertainty. ")

```

Abundance and biomass throughout the survey time series are presented using numbers or kilograms of scallop per standardized tow, respectively (Figures `r paste0(fignum[2], " & ", fignum[3])`). Estimates are standardized to tows of 800 metres. `r if(params$bank %in% c("Ban", "BanIce", "Mid", "GB")) fig1foot` Tables `r paste0(tabnum[1], " & ", tabnum[2])` provide the values for the current and previous surveys, and long term medians, by size class.

[Return to bank summary](#`r paste0(params$bank, "links")`)
\newpage


## Shell height frequencies {#`r paste0(params$bank, "SHF")`}

For `r bankname` in `r year`, the size bin with the most scallop per tow was `r maxbin` mm (Figure `r fignum[4]`).

[Return to bank summary](#`r paste0(params$bank, "links")`)
\newpage


## Meat weight-shell height & condition {#`r paste0(params$bank, "MWSH")`}

On `r bankname` in `r year`, the empirical meat weight-shell height relationship (Figure `r fignum[5]`) estimated that a scallop with a a shell height of 100mm would have a meat weight of approximately `r ScallopRound(as.numeric( highlights$thisyear[highlights$variable=="fittedmw100mm" & highlights$bank==params$bank]),2)` grams. The modelled (GAMM) condition factor estimate `r highlights$word[highlights$variable=="CF" & highlights$bank==params$bank]` from `r highlights$lastyear[highlights$variable=="CF" & highlights$bank==params$bank]` in the previous survey (`r yeartable$lastyear[yeartable$bank == params$bank]`), to `r highlights$thisyear[highlights$variable=="CF" & highlights$bank==params$bank]` in `r year`, and was `r mwshltm` the long term median of `r highlights$LTM[highlights$variable=="CF" & highlights$bank==params$bank]`.

[Return to bank summary](#`r paste0(params$bank, "links")`)
\newpage


## Spatial distribution maps {#`r paste0(params$bank, "map")`}

**Pre-recruit, recruit, and fully-recruited abundance:**

The spatial distribution of pre-recruit, recruit, and fully-recruited scallop are shown in Figures `r fignum[6]` - `r fignum[8]`, and statistical summaries are in Table `r tabnum[3]`. Maps are based on a geostatistical model that uses a Gaussian Markov Random Field (GMRF) to predict the spatial distribution. These models may not represent the full range of values observed during the survey.

[Return to bank summary](#`r paste0(params$bank, "links")`)
\newpage

**Condition factor and meat count:**  

The spatial distribution of condition factor is shown in Figure `r fignum[9]`, and the spatial distribution of meat count is shown in Figure `r fignum[10]`. Statistical summaries of condition factor and meat count are provided in Table `r tabnum[4]`. Maps are based on a geostatistical model that uses a Gaussian Markov Random Field (GMRF) to predict the spatial distribution. These models may not represent the full range of values observed during the survey.

[Return to bank summary](#`r paste0(params$bank, "links")`)
\newpage

## Clapper time series {#`r paste0(params$bank, "clap")`}

Patterns in natural mortality are represented by the percentage of clappers (dead scallop, with empty hinged shells) caught in the survey tows. The percentage is calculated as the number of clappers in each size class relative to the total of dead and live scallop caught in that size class (Figure `r fignum[11]`). Survey tows are standardized to 800 metres. `r if(params$bank %in% c("Ban", "BanIce", "Mid", "GB")) fig1foot` Table `r tabnum[5]` provides the plotted values for the current and previous surveys, and long term medians, by size class.

[Return to bank summary](#`r paste0(params$bank, "links")`)
\newpage

## Biomass, meat count, and shell height relationship {#`r paste0(params$bank, "breakdown")`}

Figure `r fignum[12]` provides an overview of the relationship between biomass, meat count, and shell height, by showing the biomass for each shell height bin and the meat count for each shell height bin. Scallop with shell heights of `r highlights$thisyear[highlights$variable=="sh_for_mcreg" & highlights$bank==params$bank]` mm and above at the time of the survey would result in meat counts at or below the regulation (`r sizes$mc[sizes$bank==params$bank]$size`).

[Return to bank summary](#`r paste0(params$bank, "links")`)
