---
output:
  officedown::rdocx_document
params:
  bank: NA
  banknum: NA
header-includes:
 - \usepackage{float}
---


```{r, echo=F, include=F, message=F, warning=F}
knitr::opts_knit$set(eval.after = "fig.cap")

options(knitr.kable.NA = '')
require(tidyverse)
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
library(officedown)

year <- 2021

load("summary3.Rdata")
source(paste0(direct_fns, "/Other_functions/ScallopRound.R"))

ntows <- summary_data$ntows
highlights <- summary_data$highlights
sizes <- summary_data$sizes
dates <- summary_data$dates
yeartable <- summary_data$yeartable
spatial.sum.stats <- summary_data$spatial.sum.stats

bank <- data.frame(lab = c("Ban", "BanIce", "Mid", "Sab", "Ger", "BBn", "BBs", "GB", "GBa", "GBb"), name=NA)
bank$name[bank$lab=="Ban"] <- "Banquereau (Sea scallop)"
bank$name[bank$lab=="BanIce"] <- "Banquereau (Icelandic scallop)"
bank$name[bank$lab=="Mid"] <- "Middle Bank"
bank$name[bank$lab=="Sab"] <- "Sable Bank"
bank$name[bank$lab=="Ger"] <- "German Bank"
bank$name[bank$lab=="BBn"] <- "Browns Bank North"
bank$name[bank$lab=="BBs"] <- "Browns Bank South"
bank$name[bank$lab=="GB"] <- "Georges Bank (monitoring stations)"
bank$name[bank$lab=="GBa"] <- "Georges Bank 'a'"
bank$name[bank$lab=="GBb"] <- "Georges Bank 'b'"

bankname <- bank$name[bank$lab==params$bank]
bank$towtype1[bank$lab %in% c("Ban", "BanIce", "GB", "Mid")] <- "fixed"
bank$towtype1[bank$lab %in% c("BBn", "BBs", "GBa", "GBb", "Sab")] <- "stratified random"
bank$towtype1[bank$lab=="Ger"] <- "random"

if(length(ntows$Freq[ntows$bank==params$bank])==2 & !params$bank %in% c("Ger", "GB")) surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==1], " ", bank$towtype1[bank$lab==params$bank],  " stations, and ", ntows$Freq[ntows$bank==params$bank & !ntows$Var1==1], " ", "exploratory stations.")
if(length(ntows$Freq[ntows$bank==params$bank])==1 & !params$bank == "Ger") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==1], " ", bank$towtype1[bank$lab==params$bank],  " stations.")
if(length(ntows$Freq[ntows$bank==params$bank])==2 & params$bank == "Ger") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==1], " ", bank$towtype1[bank$lab==params$bank],  " stations within the survey domain, and ", ntows$Freq[ntows$bank==params$bank & ntows$Var1==3], " ", "stations repeated from the previous survey.")
if(length(ntows$Freq[ntows$bank==params$bank])>2 & params$bank == "Ger") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==1], " ", bank$towtype1[bank$lab==params$bank],  " stations within the survey domain, ", ntows$Freq[ntows$bank==params$bank & ntows$Var1==3], " ", "stations repeated from the previous survey, and ", ntows$Freq[ntows$bank==params$bank & !ntows$Var1 %in% c(1, 3)], " exploratory stations.")
if(length(ntows$Freq[ntows$bank==params$bank])==2 & params$bank =="GB") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==3], " ", bank$towtype1[bank$lab==params$bank],  " stations, and ", ntows$Freq[ntows$bank==params$bank & !ntows$Var1==3], " ", "exploratory stations.")
if(length(ntows$Freq[ntows$bank==params$bank])==1 & params$bank =="GB") surv.description <- paste0(ntows$Freq[ntows$bank==params$bank & ntows$Var1==3], " ", bank$towtype1[bank$lab==params$bank],  " stations.")


if(params$bank=="Ger") {
  bank$towtype1[bank$lab==params$bank] <- "sampling with partial replacement"
  ltm_ts <- "The horizontal dashed lines are the long term medians."
}

if(!params$bank=="Ger") {
  ltm_ts <- "The dashed line is the long term median."
}

maxbin <- strsplit(highlights$word[highlights$variable=="maxbin" & highlights$bank==params$bank], "(", fixed=T)[[1]][1]

mwshltm <- strsplit(highlights$nearLTM[highlights$variable=="CF" & highlights$bank==params$bank], " (", fixed=T)[[1]][1]

tabnum <- 5*(params$banknum-1) + 1:5
fignum <- 12*(params$banknum-1) + 1:12

sumtable <- highlights[#highlights$bank==params$bank & 
  highlights$variable %in% c("NPR", "NR", "N", "IPR", "IR", "I"), ]

sumtable$word[as.numeric(sumtable$thisyearraw) < as.numeric(sumtable$lastyearraw)] <- "decreased"
sumtable$word[as.numeric(sumtable$thisyearraw) > as.numeric(sumtable$lastyearraw)] <- "increased"

sumtable$perc[sumtable$word=="increased"] <- 
  (as.numeric(sumtable$thisyearraw[sumtable$word=="increased"]) - as.numeric(sumtable$lastyearraw[sumtable$word=="increased"]))/
  as.numeric(sumtable$thisyearraw[sumtable$word=="increased"]) *100

sumtable$perc[sumtable$word=="decreased"] <-   
  (as.numeric(sumtable$lastyearraw[sumtable$word=="decreased"]) - as.numeric(sumtable$thisyearraw[sumtable$word=="decreased"]))/
  as.numeric(sumtable$lastyearraw[sumtable$word=="decreased"]) *100

sumtable$perclab <- ScallopRound(sumtable$perc, 2)

sumtable$perclab[sumtable$perc>0 & sumtable$perc < 0.01] <- "<0.01"
sumtable$perclab[sumtable$perc>99] <- ">99"

sumtable$state <- paste0(sumtable$word, " by ", sumtable$perclab, "% since")

sumtable$state[is.na(sumtable$perc)] <- "was similar to"

highlights$lastyear[highlights$variable %in% c("N", "NR", "NPR", "I", "IR", "IPR", "Nclap", "NRclap", "NPRclap", "PRpercentclap", "Rpercentclap", "Cpercentclap") & !is.na(highlights$lastyearraw) & (highlights$lastyearraw>0 & highlights$lastyearraw<0.01)] <- "<0.01"
highlights$thisyear[highlights$variable %in% c("N", "NR", "NPR", "I", "IR", "IPR", "Nclap", "NRclap", "NPRclap", "PRpercentclap", "Rpercentclap", "Cpercentclap") & !is.na(highlights$thisyearraw) & (highlights$thisyearraw>0 & highlights$thisyearraw<0.01)] <- "<0.01"
highlights$LTM[highlights$variable %in% c("N", "NR", "NPR", "I", "IR", "IPR", "Nclap", "NRclap", "NPRclap", "PRpercentclap", "Rpercentclap", "Cpercentclap") & !is.na(highlights$LTMraw) & (highlights$LTMraw>0 & highlights$LTMraw<0.01)] <- "<0.01"

highlights$word[highlights$variable=="CF" & highlights$bank==params$bank & highlights$word=="was similar"] <- "was similar to"
highlights$word[highlights$variable=="CF" & highlights$bank==params$bank & highlights$word=="increased"] <- "increased since"
highlights$word[highlights$variable=="CF" & highlights$bank==params$bank & highlights$word=="decreased"] <- "decreased since"

if(grepl(pattern = "increase", x = highlights$word[highlights$variable=="CF" & highlights$bank==params$bank])==T) cf_statement <-
  paste0("increased from ", highlights$lastyear[highlights$variable=="CF" & highlights$bank==params$bank], " in the previous survey (", yeartable$lastyear[yeartable$bank == params$bank], "), to ", highlights$thisyear[highlights$variable=="CF" & highlights$bank==params$bank], " in ", year)

if(grepl(pattern = "decrease", x = highlights$word[highlights$variable=="CF" & highlights$bank==params$bank])==T) cf_statement <-
  paste0("decreased from ", highlights$lastyear[highlights$variable=="CF" & highlights$bank==params$bank], " in the previous survey (", yeartable$lastyear[yeartable$bank == params$bank], "), to ", highlights$thisyear[highlights$variable=="CF" & highlights$bank==params$bank], " in ", year)

if(grepl(pattern = "similar", x = highlights$word[highlights$variable=="CF" & highlights$bank==params$bank])==T) cf_statement <-
  paste0("was similar to the previous survey (",  highlights$lastyear[highlights$variable=="CF" & highlights$bank==params$bank], " in ", yeartable$lastyear[yeartable$bank == params$bank], "), at ", highlights$thisyear[highlights$variable=="CF" & highlights$bank==params$bank], " in ", year)

if(params$bank %in% c("Ban", "BanIce", "Mid", "GB")) fig1foot <- paste0("Note that error bars are not calculated for fixed station survey designs as they do not properly account for uncertainty. ")
```


\newpage


# `r bankname`

## Survey Design & Analysis

The survey of `r bankname` in `r year` used a `r bank$towtype1[bank$lab==params$bank]` survey design (Figure `r fignum[1]`). There were `r surv.description`

_In the `r bankname` survey, pre-recruits are considered to be scallops with shell heights less than `r sizes$RS[sizes$bank==params$bank]$size` mm, recruits have shell heights from `r sizes$RS[sizes$bank==params$bank]$size` mm to `r (sizes$CS[sizes$bank==params$bank]$size)-1` mm, and fully-recruited scallop have shell heights greater than or equal to `r sizes$CS[sizes$bank==params$bank]$size` mm._


## Abundance & biomass time series summary 

Abundance and biomass throughout the survey time series are presented using numbers or kilograms of scallop per standardized tow, respectively.   

-  Pre-recruit abundance `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "NPR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "NPR"]` the long term median. 
-  Recruit abundance `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "NR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "NR"]` the long term median.
-  Fully-recruited abundance `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "N"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "N"]` the long term median.


-  Pre-recruit biomass `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "IPR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "IPR"]` the long term median.
-  Recruit biomass `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "IR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "IR"]` the long term median.
-  Fully-recruited biomass `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "I"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "I"]` the long term median.

_Estimates are standardized to tows of 800 metres. `r if(params$bank %in% c("Ban", "BanIce", "Mid", "GB")) fig1foot` Tables `r paste0(tabnum[1], " & ", tabnum[2])` provide the values for the current and previous surveys, and long term medians, by size class._

```{r, echo=F, tab.cap="Number of scallop per standardized tow by size class, for the current survey, previous survey, and long term median."}
table <- highlights[highlights$bank==params$bank & highlights$variable %in% c("NPR", "NR", "N"), c("variable", "lastyear", "thisyear", "LTM")]
table$variable <- c(paste0("Pre-recruits (<", sizes$RS[sizes$bank==params$bank]$size, "mm)"),
                    paste0("Recruits (", sizes$RS[sizes$bank==params$bank]$size, "-", (sizes$CS[sizes$bank==params$bank]$size-1), "mm)"),
                    paste0("Fully-recruited ($\\geq$", sizes$CS[sizes$bank==params$bank]$size, "mm)"))
names(table) <- c("Size class", paste0(yeartable[yeartable$bank==params$bank, "lastyear"], " survey"), paste0(yeartable[yeartable$bank==params$bank, "currentyear"], " survey"), "Long term median")
rownames(table) <- NULL

table
```


```{r, echo=F, tab.cap="Kilograms (kg) of scallop per standardized tow by size class, for the current survey, previous survey, and long term median."}
table <- highlights[highlights$bank==params$bank & highlights$variable %in% c("IPR", "IR", "I"), c("variable", "lastyear", "thisyear", "LTM")]
table$variable <- c(paste0("Pre-recruits (<", sizes$RS[sizes$bank==params$bank]$size, "mm)"),
                    paste0("Recruits (", sizes$RS[sizes$bank==params$bank]$size, "-", (sizes$CS[sizes$bank==params$bank]$size-1), "mm)"),
                    paste0("Fully-recruited ($\\geq$", sizes$CS[sizes$bank==params$bank]$size, "mm)"))
names(table) <- c("Size class", paste0(yeartable[yeartable$bank==params$bank, "lastyear"], " survey"), paste0(yeartable[yeartable$bank==params$bank, "currentyear"], " survey"), "Long term median")
rownames(table) <- NULL

table

```

## Shell height frequencies 

For `r bankname` in `r year`, the size bin with the most scallop per tow was `r maxbin` mm (Figure `r fignum[4]`).

## Meat weight-shell height & condition {#`r paste0(params$bank, "MWSH")`}

On `r bankname` in `r year`, the empirical meat weight-shell height relationship (Figure `r fignum[5]`) estimated that a scallop with a shell height of 100mm would have a meat weight of approximately `r ScallopRound(as.numeric( highlights$thisyear[highlights$variable=="fittedmw100mm" & highlights$bank==params$bank]),2)` grams. The modelled (GAMM) condition factor estimate `r cf_statement`, and was `r mwshltm` the long term median of `r highlights$LTM[highlights$variable=="CF" & highlights$bank==params$bank]`.


## Spatial distribution maps 

```{r, echo=F}
spatial.stats.abund <- spatial.sum.stats$abund[spatial.sum.stats$abund$bank==params$bank, c("Min.", "Median", "Mean", "Max.")]
rownames(spatial.stats.abund) <- NULL 
names(spatial.stats.abund) <- c("Minimum", "Median", "Mean", "Maximum")
spatial.stats.abund$`Size class` <- c("Pre-recruits", "Recruits", "Fully-recruited")
spatial.stats.abund <- spatial.stats.abund[,c(5,1:4)]

spatial.stats.detail <- spatial.sum.stats$cf[spatial.sum.stats$cf$bank==params$bank, c("Min.", "Median", "Mean", "Max.")]
rownames(spatial.stats.detail) <- NULL 
names(spatial.stats.detail) <- c("Minimum", "Median", "Mean", "Maximum")
spatial.stats.detail$` ` <- c("Condition factor")
spatial.stats.detail <- spatial.stats.detail[,c(5,1:4)]

mc <- spatial.sum.stats$mc[spatial.sum.stats$mc$bank==params$bank, c("Min.", "Median", "Mean", "Max.")]
rownames(mc) <- NULL
names(mc) <- c("Minimum", "Median", "Mean", "Maximum")
mc$` ` <- c("Meat count")
mc <- mc[,c(5,1:4)]
spatial.stats.detail <- rbind(spatial.stats.detail, mc)


```

**Pre-recruit, recruit, and fully-recruited abundance:**

The spatial distributions of pre-recruit, recruit, and fully-recruited scallop are shown in the upcoming maps. The colours are based on a geostatistical model that uses a Gaussian Markov Random Field (GMRF) to predict the spatial distribution.  
_These models may not represent the full range of values observed during the survey._

```{r, echo=F, tab.cap="Summary statistics for tow abundance by size class, for the current survey."}
table <- spatial.stats.abund
table$`Size class` <- c(paste0("Pre-recruits (<", sizes$RS[sizes$bank==params$bank]$size, "mm)"),
                    paste0("Recruits (", sizes$RS[sizes$bank==params$bank]$size, "-", (sizes$CS[sizes$bank==params$bank]$size-1), "mm)"),
                    paste0("Fully-recruited ($\\geq$", sizes$CS[sizes$bank==params$bank]$size, "mm)"))

table

```

**Condition factor and meat count:**  

_The spatial distribution of condition factor is shown in Figure `r fignum[9]`, and the spatial distribution of meat count is shown in Figure `r fignum[10]`. Statistical summaries of condition factor and meat count are provided in Table `r tabnum[4]`. Maps are based on a geostatistical model that uses a Gaussian Markov Random Field (GMRF) to predict the spatial distribution. These models may not represent the full range of values observed during the survey._

```{r, echo=F, tab.cap="Summary statistics for condition factor and meat count for the current survey."}
table <- spatial.stats.detail

table

```


## Clapper time series 

Patterns in natural mortality are represented by the percentage of clappers (dead scallop, with empty hinged shells) caught in the survey tows.  
_The percentage is calculated as the number of clappers in each size class relative to the total of dead and live scallop caught in that size class (Figure `r fignum[11]`). Survey tows are standardized to 800 metres. `r if(params$bank %in% c("Ban", "BanIce", "Mid", "GB")) fig1foot` Table `r tabnum[5]` provides the plotted values for the current and previous surveys, and long term medians, by size class._

```{r, echo=FALSE, message=F, tab.cap="Percentage of clappers per standardized tow by size class, for the current survey, previous survey, and long term median."}
table <- highlights[highlights$bank==params$bank & highlights$variable %in% c("PRpercentclap", "Rpercentclap", "Cpercentclap"), c("variable", "lastyear", "thisyear", "LTM")]
table$variable <- c(paste0("Pre-recruits (<", sizes$RS[sizes$bank==params$bank]$size, "mm)"),
                    paste0("Recruits (", sizes$RS[sizes$bank==params$bank]$size, "-", (sizes$CS[sizes$bank==params$bank]$size-1), "mm)"),
                    paste0("Fully-recruited ($\\geq$", sizes$CS[sizes$bank==params$bank]$size, "mm)"))
names(table) <- c("Size class", paste0(yeartable[yeartable$bank==params$bank, "lastyear"], " survey"), paste0(yeartable[yeartable$bank==params$bank, "currentyear"], " survey"), "Long term median")
rownames(table) <- NULL

table
```


## Biomass, meat count, and shell height relationship 

Figure `r fignum[12]` provides an overview of the relationship between biomass, meat count, and shell height, by showing the biomass for each shell height bin and the meat count for each shell height bin. Scallop with shell heights of `r highlights$thisyear[highlights$variable=="sh_for_mcreg" & highlights$bank==params$bank]` mm and above at the time of the survey would result in meat counts at or below the regulation (`r sizes$mc[sizes$bank==params$bank]$size`).

**`r year` Summary**

-  Pre-recruit abundance `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "NPR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "NPR"]` the long term median. 
-  Recruit abundance `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "NR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "NR"]` the long term median.
-  Fully-recruited abundance `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "N"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "N"]` the long term median.


-  Pre-recruit biomass `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "IPR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "IPR"]` the long term median.
-  Recruit biomass `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "IR"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "IR"]` the long term median.
-  Fully-recruited biomass `r sumtable$state[sumtable$bank==params$bank & sumtable$variable == "I"]` `r yeartable$lastyear[yeartable$bank == params$bank]`, and was `r sumtable$nearLTM[sumtable$bank==params$bank & sumtable$variable == "I"]` the long term median.


- Condition factor `r paste0(highlights$word[highlights$variable=="CF" & highlights$bank==params$bank], " ", yeartable$lastyear[yeartable$bank == params$bank])`, and was `r mwshltm` the long term median.
